Binning Strategies and Related Loss for Large Data

### 2015-03-01 Paper.Rnw
Update hadley and liu et al paragraph introducing binning to reduce graphical complexity/computational benefits.

One approach to reduce the graphical complexity is to bin the displayed data. This has the additional advantage of reducing the size of the stored data, as only the bin centers and the frequency of points which correspond to that bin must be stored. \ktm{ Add \citep{Wickham2013Bin}  \citep{Liu2013imMens} here to argue the merits of binning. } \hh{also add \ref{gold} for binning reference - it's called `weighting' there.}

>>>>

\ktm{ Another approach is to reduce the graphical complexity by plotting binned aggregations, namely frequencies, of the data as opposed to plotting every observation as an individual point.} This has the additional advantage of reducing the size of the stored data \ktm{necessary for the construction of the plot}, as only the bin centers and the frequency of points which correspond to that bin must be stored. \ktm{ Wickham argues for a ``bin-summarize-smooth'' procedure to to be applied to the visualization of big data and notes that simple summary functions, such as counts, scale very well with the size of data sources \citep{Wickham2013Bin}. Liu, Jiang and Heer employ the computational benefits of binning for their interactive big data visualization program, \textit{imMens} \citep{Liu2013imMens}. } \hh{also add \citep{gold} for binning reference - it's called `weighting' there.}
